Tree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-10-08 manuscript/climate_sensitivity_draft.Rmd
quick fix on table 2
No longer trying to format in LaTEX. We will need to change this at the proof stage.

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/variables_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "**Table 2. Summary of variables**", format = 'latex', escape = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," "," ", "observed values" = 3, " ")) %>%
  column_spec(4, width = "7cm") %>%
  pack_rows("Dependent variable", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Independent variables", 2, 18, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("tree size", 5, 6, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("microhabitat", 7, 11, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("species' traits", 12, 18, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  kable_styling()
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/variables_table.csv", stringsAsFactors = FALSE, check.names = FALSE)

kable(hypothesis_table, booktabs = TRUE, caption = "**Table 2. Summary of variables**", format = 'latex', escape = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," "," ", "observed values" = 3, " ")) %>%
  column_spec(4, width = "7cm") %>%
  pack_rows("Dependent variable", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Independent variables", 2, 18, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("tree size", 5, 6, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("microhabitat", 7, 11, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("species' traits", 12, 18, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  kable_styling()
```
